Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2023-11-27 article.qmd
Remove subsection
Add example of limitation of just controlling from Python
Add CSS to justify

---
title: "Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems."
bibliography: bibliography.bib
format:
  html:
    number-sections: true
    anchor-sections: true
  pdf:
    documentclass: scrartcl
    papersize: a4
    geometry:
        - margin=20mm
    pdf-engine: tectonic
    number-sections: true
    colorlinks: true
  docx:
    number-sections: true
---

@@

One limitation of these tools is that they are not extensible from Python,
as they are either built on or use wrapped libraries in other languages.
This means that they allow you to "control" the model definition and simulation in a Python script,
but you cannot use other packages from the vast Python community to change the way the simulation is carried out.
In a way, we could say that
they make it easier to avoid having to export the simulation results to a CSV file
and then load them into Python for further analysis.
TODO: GIVE EXAMPLES

@@

Modular code architecture makes code reusable, extensible, and easier to maintain.
Therefore, we split the code to define and simulate reaction systems into three Python packages:
symbolite, to create symbolic expressions;
poincaré, to define dynamical systems;
and simbio, to define reaction systems and interface with systems biology standards such as SBML.
TODO: NOT SURE SUBSECTIONS ARE A GOOD IDEA. MAYBE JUST BOLD

## Symbolite

>>>>

---
title: "Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems."
bibliography: bibliography.bib
format:
  html:
    number-sections: true
    anchor-sections: true
    css: article.css
  pdf:
    documentclass: scrartcl
    papersize: a4
    geometry:
        - margin=20mm
    pdf-engine: tectonic
    number-sections: true
    colorlinks: true
  docx:
    number-sections: true
---

@@

One limitation of these tools is that they are not extensible from Python,
as they are either built on or use wrapped libraries in other languages.
This means that they allow you to "control" the model definition and simulation in a Python script,
but you cannot use other packages from the vast Python community to change the way the simulation is carried out.
For instance,
to do a Random Parameter Scan in COPASI,
we must choose between one of the predefined distributions,
but cannot use one of the meny distributions from `scipy.stats`.
In a way, we could say that
they make it easier to avoid having to export the simulation results to a CSV file
and then load them into Python for further analysis.

@@

Modular code architecture makes code reusable, extensible, and easier to maintain.
Therefore, we split the code to define and simulate reaction systems into three Python packages:
symbolite, to create symbolic expressions;
poincaré, to define dynamical systems;
and simbio, to define reaction systems and interface with systems biology standards such as SBML.
